---
title: "Differential Analysis of CC7 H2 CC7-SSB01 Temperature RNAseq data"
author: "cuig"
date: "July 31, 2016"
output:
  html_document:
    toc: true
    toc_depth: 5
    toc_float: true
    theme: united
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


`kallisto index -i aip.genome_models.mRNA.idx aip.genome_models.mRNA.fa`

> 
```
[build] loading fasta file aip.genome_models.mRNA.fa
[build] k-mer length: 31
[build] warning: clipped off poly-A tail (longer than 10)
        from 13 target sequences
[build] warning: replaced 1305686 non-ACGUT characters in the input sequence
        with pseudorandom nucleotides
[build] counting k-mers ... done.
[build] building target de Bruijn graph ...  done
[build] creating equivalence classes ...  done
[build] target de Bruijn graph has 482414 contigs and contains 62901627 k-mers
```


```
for a in CC7 H2 SSB01; do for b in 25 32; do for c in {1..4}; do kallisto quant -i aip.genome_models.mRNA.idx -o kallisto/${a}-${b}-${c}/ --single -l 200 -s 20 -b 100 -t 32 raw_reads/*${a}-${b}-${c}*.fastq; done; done; done
```

## load libraries
```{r,message=FALSE}
library(dplyr)
library(tidyr)
library(ggplot2)
library(ggfortify)
library(sleuth)
library(UpSetR)
library(pheatmap)
```

## prepare sample tables for the analysis
```{r}
base_dir <- 'BASE_DIR'

setwd(base_dir)
sample_id <- dir(file.path(base_dir, "kallisto"))
kal_dirs <- sapply(sample_id, function(id) file.path(base_dir, 'kallisto', id))
s2c <- data.frame(sample = sample_id, 
                  host = rep(c("CC7", "H2", "CC7"), each = 8), 
                  symbiont = rep(c("A", "B", "B"), each = 8),
                  temp = rep(c("25", "32"), each = 4))
s2c$condition <- paste(s2c$host, s2c$symbiont, s2c$temp, sep = "")
s2c <- dplyr::mutate(s2c, path = kal_dirs)
s2c_cc7 <- s2c[c(1:8, 17:24),]
```


## cc7_temp32_vs_temp25
### load data from kallisto - sleuth log
```{r}
cc7_temp32_vs_temp25 <- sleuth::sleuth_prep(s2c[1:8,], ~ temp)
cc7_temp32_vs_temp25 <- sleuth::sleuth_fit(cc7_temp32_vs_temp25)
cc7_temp32_vs_temp25 <- sleuth::sleuth_wt(cc7_temp32_vs_temp25, 'temp32')
```

### extract data from sleuth output
- **kallisto table (kt)**
```{r}
cc7_temp32_vs_temp25_kt <- kallisto_table(cc7_temp32_vs_temp25, use_filtered = FALSE, normalized = FALSE, include_covariates = FALSE)
summary(cc7_temp32_vs_temp25_kt)
write.csv(cc7_temp32_vs_temp25_kt, file = 'cc7_temp32_vs_temp25_kt.csv', row.names = FALSE)
cc7_temp32_vs_temp25_fil_kt <- kallisto_table(cc7_temp32_vs_temp25, use_filtered = TRUE, normalized = TRUE,include_covariates = FALSE)
summary(cc7_temp32_vs_temp25_fil_kt)
write.csv(cc7_temp32_vs_temp25_fil_kt, file = 'cc7_temp32_vs_temp25_fil_kt.csv', row.names = FALSE)
```

- **result table (rt)**
```{r}
cc7_temp32_vs_temp25_rt <- sleuth_results(cc7_temp32_vs_temp25, 'temp32')
summary(cc7_temp32_vs_temp25_rt)
write.csv(cc7_temp32_vs_temp25_rt, file = 'cc7_temp32_vs_temp25_rt.csv', row.names = FALSE)
```

- **diff expr trans table (diff)**
```{r}
cc7_temp32_vs_temp25_diff <- subset(cc7_temp32_vs_temp25_rt, qval<=0.05)
dim(cc7_temp32_vs_temp25_diff)
summary(cc7_temp32_vs_temp25_diff)
write.csv(cc7_temp32_vs_temp25_diff, file = 'cc7_temp32_vs_temp25_diff.csv', row.names = FALSE)
cc7_temp32_vs_temp25_diff_id <- cc7_temp32_vs_temp25_diff[,1]
write.csv(cc7_temp32_vs_temp25_diff_id, file = 'cc7_temp32_vs_temp25_diff_id.csv', row.names = FALSE)
```


## h2_temp32_vs_temp25
### load data from kallisto - sleuth log
```{r}
h2_temp32_vs_temp25 <- sleuth::sleuth_prep(s2c[10:16,], ~ temp)
h2_temp32_vs_temp25 <- sleuth::sleuth_fit(h2_temp32_vs_temp25)
h2_temp32_vs_temp25 <- sleuth::sleuth_wt(h2_temp32_vs_temp25, 'temp32')
```

### extract data from sleuth output
- **kallisto table (kt)**
```{r}
h2_temp32_vs_temp25_kt <- kallisto_table(h2_temp32_vs_temp25, use_filtered = FALSE, normalized = FALSE, include_covariates = FALSE)
summary(h2_temp32_vs_temp25_kt)
write.csv(h2_temp32_vs_temp25_kt, file = 'h2_temp32_vs_temp25_kt.csv', row.names = FALSE)
h2_temp32_vs_temp25_fil_kt <- kallisto_table(h2_temp32_vs_temp25, use_filtered = TRUE, normalized = TRUE,include_covariates = FALSE)
summary(h2_temp32_vs_temp25_fil_kt)
write.csv(h2_temp32_vs_temp25_fil_kt, file = 'h2_temp32_vs_temp25_fil_kt.csv', row.names = FALSE)
```

- **result table (rt)**
```{r}
h2_temp32_vs_temp25_rt <- sleuth_results(h2_temp32_vs_temp25, 'temp32')
summary(h2_temp32_vs_temp25_rt)
write.csv(h2_temp32_vs_temp25_rt, file = 'h2_temp32_vs_temp25_rt.csv', row.names = FALSE)
```

- **diff expr trans table (diff)**
```{r}
h2_temp32_vs_temp25_diff <- subset(h2_temp32_vs_temp25_rt, qval<=0.05)
dim(h2_temp32_vs_temp25_diff)
summary(h2_temp32_vs_temp25_diff)
write.csv(h2_temp32_vs_temp25_diff, file = 'h2_temp32_vs_temp25_diff.csv', row.names = FALSE)
h2_temp32_vs_temp25_diff_id <- h2_temp32_vs_temp25_diff[,1]
write.csv(h2_temp32_vs_temp25_diff_id, file = 'h2_temp32_vs_temp25_diff_id.csv', row.names = FALSE)
```


## ssb01_temp32_vs_temp25
### load data from kallisto - sleuth log
```{r}
ssb01_temp32_vs_temp25 <- sleuth::sleuth_prep(s2c[17:24,], ~ temp)
ssb01_temp32_vs_temp25 <- sleuth::sleuth_fit(ssb01_temp32_vs_temp25)
ssb01_temp32_vs_temp25 <- sleuth::sleuth_wt(ssb01_temp32_vs_temp25, 'temp32')
```

### extract data from sleuth output
- **kallisto table (kt)**
```{r}
ssb01_temp32_vs_temp25_kt <- kallisto_table(ssb01_temp32_vs_temp25, use_filtered = FALSE, normalized = FALSE, include_covariates = FALSE)
summary(ssb01_temp32_vs_temp25_kt)
write.csv(ssb01_temp32_vs_temp25_kt, file = 'ssb01_temp32_vs_temp25_kt.csv', row.names = FALSE)
ssb01_temp32_vs_temp25_fil_kt <- kallisto_table(ssb01_temp32_vs_temp25, use_filtered = TRUE, normalized = TRUE,include_covariates = FALSE)
summary(ssb01_temp32_vs_temp25_fil_kt)
write.csv(ssb01_temp32_vs_temp25_fil_kt, file = 'ssb01_temp32_vs_temp25_fil_kt.csv', row.names = FALSE)
```

- **result table (rt)**
```{r}
ssb01_temp32_vs_temp25_rt <- sleuth_results(ssb01_temp32_vs_temp25, 'temp32')
summary(ssb01_temp32_vs_temp25_rt)
write.csv(ssb01_temp32_vs_temp25_rt, file = 'ssb01_temp32_vs_temp25_rt.csv', row.names = FALSE)
```

- **diff expr trans table (diff)**
```{r}
ssb01_temp32_vs_temp25_diff <- subset(ssb01_temp32_vs_temp25_rt, qval<=0.05)
dim(ssb01_temp32_vs_temp25_diff)
summary(ssb01_temp32_vs_temp25_diff)
write.csv(ssb01_temp32_vs_temp25_diff, file = 'ssb01_temp32_vs_temp25_diff.csv', row.names = FALSE)
ssb01_temp32_vs_temp25_diff_id <- ssb01_temp32_vs_temp25_diff[,1]
write.csv(ssb01_temp32_vs_temp25_diff_id, file = 'ssb01_temp32_vs_temp25_diff_id.csv', row.names = FALSE)
```

```{r}
sessionInfo()
```
